Thread Pool in GeckoDB/BOLSTER - Integrating a Thread Pool into a high performance Database System \\

### 2018-06-20 Presentations/Paper/paper_thread_pool.tex
Add tbb and gtest references to paper

To overcome these drawbacks, we integrate an optimised thread pool in BOLSTER. Along with the implementation, we measure the performance of the primitives to determine the thread pool overhead. Additionally, we measure metrics like \emph{idle and job time} of threads to evaluate correct thread pool sizes for the considered use cases.  In this work we make the following contributions:
\begin{itemize}
	\item We describe our design and implementation of the thread pool 
	\item We evaluate the possibility to wait for a group of task in the calling thread
	\item We compare our thread pool against the existing implementation in BOLSTER
\end{itemize}
We organized the rest of the paper as follows. In Section 2, we give preliminaries about the considered task configuration and about thread safe access of memory. In Section 3, we show our design and implementation of the thread pool and examine our experimental environment in Section 4. In Section 5, we describe the results of our performance evaluation. In Section 6, we name related work and state our conclusion and future work in Section 7.

@@

\subsubsection{Thread Pool Statistics}
To consider the thread pool instance, an important metric is the average waiting time of tasks. In order to optimize the thread pool size, a balanced relation between the waiting time of tasks and the number of threads must be found. Furthermore, at a specific time, the relation between enqueued and completed tasks can be interesting. In Table \ref{tab4}, we show our statistics collected for each thread pool instance.

@@

We will use these statistics to adapt our thread pool implementation to different use cases later on. In the next sections, we define our experimental environment, the implementation of our tests including the measured metrics and the test results.

@@

Furthermore, we compare the scope and usage of our thread pool against an existing implementation \emph{Threading Building Blocks (Intel TBB)} \textbf{TODO: cite!} written in C++. Since Intel TBB uses completely different approaches to parallel the execution of tasks, a direct performance comparison may not lead to reliable results. Therefore, we evaluate the usage and the scope both implementations give.

>>>>

To overcome these drawbacks, we integrate an optimised thread pool in BOLSTER. Along with the implementation, we measure the performance of the primitives to determine the thread pool overhead. Additionally, we measure metrics like \emph{waiting and busy time} of threads to evaluate correct thread pool sizes for the considered use cases.  In this work we make the following contributions:
\begin{itemize}
	\item We describe our design and implementation of the thread pool 
	\item We evaluate the possibility to wait for a group of task in the calling thread
	\item We compare our thread pool against the existing implementation in BOLSTER
\end{itemize}
We organized the rest of the paper as follows. In Section 2, we give preliminaries about the considered task configuration and about thread safe access of memory. In Section 3, we show our design and implementation of the thread pool and examine our experimental environment in Section 4. In Section 5, we describe the results of our performance evaluation. In Section 6, we name related work and state our conclusion and future work in Section 7.

@@

\subsubsection{Thread Pool Statistics}
To consider the thread pool instance, an important metric is the average waiting time of tasks. In order to optimize the thread pool size, a balanced relation between the waiting time of tasks and the number of threads must be found. Furthermore, at a specific time, the relation between enqueued and completed tasks can be interesting. In Table \ref{tab4}, we show our statistics collected for each thread pool instance. We will use these statistics to adapt our thread pool implementation to different use cases later on.

@@

\subsection{Testing and Memory Control}
As last aspect of our implementation, we show how we test the thread pool and how we ensure to avoid memory leaks. Since geckoDB already uses GTest \cite{sen2010quick} for unit testing, we also wrote our test using this framework.

@@

Furthermore, we compare the scope and usage of our thread pool against an existing implementation \emph{Threading Building Blocks (Intel TBB)} \cite{kim2011multicore} written in C++. Since Intel TBB uses completely different approaches to parallel the execution of tasks, a direct performance comparison may not lead to reliable results. Therefore, we evaluate the usage and the scope both implementations give.
